```{r}
#| eval: false
survey <- tar_read(siviru_survey)
cont_var <- "edad"
grp_var <- "beneficia"
cont_lbl <- "Edad"
grp_lbl <- "Exposición al proyecto"
```

```{r}
survey_dict <- c(
  setNames(cont_lbl, cont_var),
  setNames(grp_lbl, grp_var),
  ecdf = "Función de Distribución Acumulativa Empírica (ECDF)"
)
```

```{r}
efun::denstogram(
  data = survey,
  xvar = !!rlang::sym(cont_var),
  xaxis_title = cont_lbl,
  yaxis_title = "Densidad",
  summary_geom = "line",
  plotly = FALSE
) +
  ggplot2::labs(dictionary = survey_dict)
```

```{r}
efun::denstogram(
  data = survey,
  xvar = !!rlang::sym(cont_var),
  fillvar = !!rlang::sym(grp_var),
  xaxis_title = cont_lbl,
  yaxis_title = "Densidad",
  plotly = FALSE
) +
  ggplot2::labs(dictionary = survey_dict)
```

```{r}
# survey |> efun::ecdfgram(edad, grpvar = beneficia)
survey |>
  ggplot2::ggplot() +
  ggplot2::aes(x = !!rlang::sym(cont_var), color = !!rlang::sym(grp_var)) +
  ggplot2::stat_ecdf(na.rm = TRUE, linewidth = 2) +
  ggplot2::labs(dictionary = survey_dict)
```

```{r}
survey |>
  ggplot2::ggplot() +
  ggplot2::aes(
    x = !!rlang::sym(grp_var),
    y = !!rlang::sym(cont_var),
    fill = !!rlang::sym(grp_var)
  ) +
  ggplot2::geom_violin(trim = FALSE, alpha = 0.55) +
  ggplot2::geom_boxplot(width = 0.15) +
  ggforce::geom_sina(aes(color = !!rlang::sym(grp_var)), alpha = .85, size = 3) +
  stat_summary(
    fun.y = mean,
    geom = "point",
    size = 3,
    color = "red",
    show.legend = FALSE
  ) +
  ggplot2::labs(dictionary = survey_dict)
```



```{r}
# Energy test (strong omnibus power)
# sizes <- base::as.integer(base::table(df$group))
# energy::eqdist.etest(x = base::matrix(df$age, ncol = 1), sizes = sizes, R = 1999)

# Split age by group
vars_list <- base::split(survey[[cont_var]], survey[[grp_var]])

# Anderson–Darling k-sample (tail-sensitive)
# Run tests
test1 <- kSamples::ad.test(vars_list)
test2 <- stats::kruskal.test(
  formula = as.formula(paste(cont_var, "~", grp_var)),
  data = survey
)
test3 <- stats::oneway.test(
  as.formula(paste(cont_var, "~", grp_var)),
  var.equal = FALSE,
  data = survey
)


```



```{r}
# Helper to safely extract fields
get_field <- function(x, fields) {
  for (f in fields) {
    v <- base::tryCatch(base::get0(f, x, inherits = FALSE), error = function(e) NULL)
    if (!base::is.null(v)) {
      return(v)
    }
  }
  return(NA_real_)
}

# Extract stats
ad_stat <- get_field(test1, c("adk", "ad", "statistic"))
ad_p <- get_field(test1, c("adk.p.value", "p.value"))
kw_stat <- unname(test2$statistic)
kw_df <- unname(test2$parameter)
kw_p <- test2$p.value
wl_F <- unname(test3$statistic)
wl_df1 <- unname(test3$parameter[1]) # num df
wl_df2 <- unname(test3$parameter[2]) # denom df
wl_p <- test3$p.value

# Format helpers
fmt_num <- function(x) {
  if (base::is.na(x)) NA_character_ else base::formatC(x, digits = 3, format = "f")
}
fmt_p <- function(p) {
  if (base::is.na(p)) NA_character_ else base::format.pval(p, digits = 3, eps = 1e-3)
}

# Build table (as a base data.frame)
out <- base::rbind(
  base::data.frame(
    Test = "Anderson–Darling (k-sample)",
    Statistic = fmt_num(ad_stat),
    DF = "",
    `p-value` = fmt_p(ad_p),
    Note = "Omnibus: equal distributions"
  ),
  base::data.frame(
    Test = "Kruskal–Wallis",
    Statistic = fmt_num(kw_stat),
    DF = base::sprintf("df = %.0f", kw_df),
    `p-value` = fmt_p(kw_p),
    Note = "Location shift across groups (medians)"
  ),
  base::data.frame(
    Test = "Welch ANOVA",
    Statistic = base::sprintf("F = %s", fmt_num(wl_F)),
    DF = base::sprintf("df1 = %.1f, df2 = %.1f", wl_df1, wl_df2),
    `p-value` = fmt_p(wl_p),
    Note = "Means across groups (unequal variances)"
  )
)

# Render nicely
knitr::kable(out, align = "lcccl", caption = "Multi-test comparison of age by group")
```









```{r}
#| eval: false
age_split <- base::split(survey$edad, survey$beneficia)

# Kolmogorov–Smirnov
stats::ks.test(age_split[[1]], age_split[[2]])

# Anderson–Darling k-sample (more tail-sensitive)
kSamples::ad.test(age_split)

# Energy test (omnibus); x must be matrix/dist, pass sizes explicitly
n_per <- base::table(survey$beneficia)
energy::eqdist.etest(
  x = base::matrix(survey$edad, ncol = 1),
  sizes = base::as.integer(n_per),
  R = 1999
)

```



If you only care about central tendency (not full shape):

# Kruskal–Wallis (nonparametric k-group location test)
stats::kruskal.test(age ~ group, data = df)

# Welch one-way ANOVA (means, unequal variances)
onewaytests::welch.test(age ~ group, data = df)  # or stats::oneway.test(..., var.equal=FALSE)





3) Post-hoc pairwise (only if the global test is significant)
a) Location shifts (medians)
stats::pairwise.wilcox.test(df$age, df$group, p.adjust.method = "BH")

b) Full-distribution differences (energy test per pair)
pairs <- utils::combn(base::levels(df$group), 2, simplify = FALSE)
pvals <- base::numeric(base::length(pairs))
nm    <- base::character(base::length(pairs))
for (i in base::seq_along(pairs)) {
  g <- pairs[[i]]
  x <- df$age[df$group == g[1]]
  y <- df$age[df$group == g[2]]
  et <- energy::eqdist.etest(x = base::c(x, y),
                             sizes = base::c(base::length(x), base::length(y)),
                             R = 1999)
  pvals[i] <- et$p.value; nm[i] <- base::paste(g, collapse = " vs ")
}
stats::p.adjust(pvals, method = "BH") |>
  stats::setNames(nm)



4) Effect sizes (report along with p-values)

Ordinal effect (robust), pairwise: Vargha–Delaney 
𝐴
A or Cliff’s delta

eff_fun <- function(a, b) effsize::VD.A(a, b)  # or effsize::cliff.delta(a, b)
es <- base::lapply(pairs, function(g) eff_fun(df$age[df$group==g[1]],
                                              df$age[df$group==g[2]]))
base::setNames(es, nm)


Mean-based global effect: eta-squared from one-way ANOVA (if means matter)

fit <- stats::aov(age ~ group, data = df)
ss  <- summary(fit)[[1]][["Sum Sq"]]
eta2 <- ss[1] / base::sum(ss); eta2  # proportion of variance explained by group

5) Compact per-group summary (sanity check)
df |>
  dplyr::group_by(group) |>
  dplyr::summarise(n = dplyr::n(),
                   mean = base::mean(age, na.rm=TRUE),
                   sd = stats::sd(age, na.rm=TRUE),
                   median = stats::median(age, na.rm=TRUE),
                   q25 = stats::quantile(age, 0.25, na.rm=TRUE),
                   q75 = stats::quantile(age, 0.75, na.rm=TRUE))



